Probabilistic Network Latency Verification

### 2023-02-14 paper/4_temporal.tex
[Paper] updated various things

\subsection{Latency Measurement as Distribution}
% To form the required latency distribution

% iid

% independent

@@

In our example, we define $l_q(EZ)$ to be lognormal distribution, which doesn't have a closed form convolution 
solution with the other latency distribution in the network, which is of gamma distribution form.
Therefore, in order to convolve two arbitrary distributions, we need to leverage a numerical convolution 
method.

We leverage an existing numerical convolution algorithm, DIRECT, to fulfill this role.
%TODO: describe DIRECT in one sentence
We choose this method due to their bounded error property: DIRECT guarantee that the computed 
distribution and the correct theoretical distribution has a KL-divergence below a certain bound.
DIRECT has also been implemented in R's popular bayesmeta package.
%TODO: cite and change font?

@@

As an ilustration, if we had 3 random variables $A$, $B$, and  $C$, and we want 
to convolve them all together, it would be faster to compute $direct(direct(A, B), C)$ instead of 
$direct(C, direct(A, B))$.

While this problem is trivial to solve (swap the input parameter if the latter is detected as a 
DIRECT distribution), it does limit the type of optimization that we could have in the chain convolution 
process.

>>>>

\subsection{Latency Measurement as Distribution}
To have the required latency distribution for $l_p$ and $l_q$, we form an empirical distribution 
from latency measurement information.
This measurement information might come in the form of packet inter-arrival time, 
queue length, and other data that is similar in nature.

Since packet inter-arrival time represent the effect of various traffic shaping mechanism on 
the many traffics on the network, we could obtain such data from published works like 
\cite{dctcp}\cite{swift}.
Central to our model is the assumption that the latency introduced by the covered component is 
i.i.d. and are independent of one another.

@@

In our model however, we intend to use real-world empirical data to be used as latency distribution, which 
might be arbitrarily shaped.
Therefore, in order to convolve two arbitrary distributions, we need to leverage a numerical convolution 
method.

We leverage an existing numerical convolution algorithm, DIRECT \cite{direct}, to fulfill this role.
We choose this method due to their bounded error property: DIRECT guarantee that the computed 
distribution and the correct theoretical distribution has a KL-divergence below a certain bound.
DIRECT has also been implemented in R's popular bayesmeta package \cite{bayesmeta}.
%TODO: cite and change font?

DIRECT works by numericaly approximating \textit{mixture distributions} from a large mixture components.
It is done by ``binning'' the mixture component / mixing distribution and intelligently chose a single 
reference value for each bin to compute the final CDF of the resulting mixing distribution.
The amount of bins and the reference value is determined based on the error bound that the user has set.

@@

As an ilustration, if we had 3 random variables $A$, $B$, and  $C$, and we want 
to convolve them all together, it would be faster to compute $direct(direct(A, B), C)$ instead of \\
$direct(C, direct(A, B))$. Trivially but importantly, we swap the input parameter if the latter is detected as a 
DIRECT distribution.

### 2023-02-14 paper/7_related.tex
[Paper] updated various things

\textbf{Network Calculus}
CCAC?

>>>>

\textbf{Network Calculus}
One promising concept with regards to performance metric verification is the theoretical 
framework of network calculus.
Network calculus aims to provide a framework to analyze the bandwidth and latency guarantee 
of a flow.
It could model link capacities, background traffic, and congestion control.
CCAC \cite{ccac}, for example, has developed a tool based on this framework to help explain 
the various behavior of a congestion control system.

While providing a strong theoretical background in latency verification, this framework 
primarily deals with guaranteeing bounds deterministically.
It also requires the user to provide more information compared to \tool, since the user 
need to provide the cummulative arrival and departure curve over time.
